(Working Title) Stellar and Planetary Properties of \KT\ \Ci\ Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving Earth-like Insolation?

### 2015-03-11 ms.tex
more changes, more to do

@@

As stated in \textsection\ref{sec:stellarparams}, we place a distance upper limit of 500 pc 
for all stars in our sample. 
Given the location of the \Ci\ field with respect to the galactic plane, we expect a low 
contamination rate by halo giants. 
However, there are a few stars that are possibly miscategorized giants.
EPIC 201257461 is identified in the RAdial Velocity Experiment (RAVE) Fourth Data Release
as a target with $\logg = 3.18$, consistent with that of a giant star.
It is therefore perhaps not surprising that this system is flagged as a false positive based on 
the transit shape.

>>>>

\anytodo{201828749 has an AO companion, flux ratio 6:1 or so. We call it a planet.
It's a very flat bottom thing, with fairly short ingress and egress: the transit shape
is way more planet than EB so I'm comfortable with this designation. We need
to talk about this though.}

@@

As stated in \textsection\ref{sec:stellarparams}, we place a distance upper limit of 500 pc 
for all stars in our sample. 
Given the location of the \Ci\ field with respect to the galactic plane, we expect a low 
contamination rate by halo giants. 
However, there are a few stars that are possibly miscategorized giants.
EPIC 201257461 is identified in the RAdial Velocity Experiment (RAVE) Fourth Data Release
as a target with $\logg = 3.18$, consistent with that of a giant star.
It is therefore perhaps not surprising that this system is flagged as a false positive based on 
the transit shape.
EPIC 201929294 has a reduced proper motion consistent with that of a giant star
